Ionization of molecules by multicharged bared ions by using the stoichiometric model

### 2019-09-15 NewMonti25.tex
atomic scaling fig added + fontsize modified

Then, by implementing the SSM and the CDW --instead of the first Born 
approximation--, we calculate ionization cross-section of several 
molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$. Furthermore, 
in Section 3, we investigate different DNA and RNA molecules
such as adenine, cytosine, guanine, thymine, uracil, and also DNA 
backbone.

@@

In Figure 1, we report our total ionization results for the six 
essential elements by the impact of six different projectiles: 
antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
To reduce the resulting 36 magnitudes into a single consistent 
figure, we considered the fact that in the first Born approximation
the ionization cross-section scales with the square of the projectile 
charge, $Z^{2}$. The values of the impact energies considered 
range between 0.1 to 10 MeV/amu, where the CDW is supposed 
to hold. In fact, for the highest projectile charges the minimum 
impact energy where the CDW is expected to be valid could be 
higher than 100 KeV. Moreover, we corroborated that the first Born 
approximation provides quite reliable results only for energies higher 
than a couple of MeV/amu. We use the same color to indicate the 
projectile charge throughout the figures of this work: dashed-red, 
solid-red, blue, magenta, olive and orange for antiprotons, 
H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$, respectively. 
Notably, there is no complete tabulation of ionization of atoms by 
the impact of multicharged ions. We hope that the ones presented 
in this article will be of help for future works.

@@

Lets us consider a molecule $M$ composed by $n_{\alpha}$ atoms of the
element $\alpha$, the SSM describes the total ionization cross section 
of the molecule $\sigma_{M}$ as a simple sum of ionization cross 
sections of the isolated atoms $\sigma_{\alpha}$, 
\begin{equation}
 \sigma_{M}=\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}\,.  
 \label{eq:sumion}
\end{equation}
We divided sixteen molecular targets of our interest in three families. 
The classification defined is given in Table~\ref{tab:families}.
\begin{table}
\begin{center}
\begin{tabular}{|p{0.06\textwidth}|p{0.62\textwidth}|}
\hline
 CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, and C$_6$H$_6$ \\
\hline
 CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, and CH$_5$N \\
\hline
 \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
                        cytosine (C$_4$H$_5$N$_2$O), \\
     & guanine (C$_5$H$_5$N$_5$O), thymine (C$_5$H$_6$N$_2$O$_2$), \\
     & uracil (C$_4$H$_4$N$_2$O$_2$), tetrahydrofuran (C$_4$H$_8$O), \\
     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
     & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
\hline
\end{tabular}
\caption{Seventeen molecular targets of our interest classified in three 
families.}
\label{tab:families}
\end{center}
\end{table}

In Figure 2, we report the total ionization cross sections by the 
impact of multicharged ions for the four fundamental DNA components: 
adenine, cytosine, guanine and thymine. Our reports for uracil and 
DNA backbone containing P are given in Figure 3. For adenine, the 
agreement with the experimental data available in our range of validity 
is quite good. For uracil, we have a puzzling situation: our results 
show good agreement with the experiments by proton impact of Itoh 
{\it et al.}~\cite{itoh2013}, but for the same target our theory fails 
by a factor of two for the impact of C$^{4+}$ and O$^{6+}$ ions. 
Nonetheless, it should be stated that our theoretical results coincide 
with calculations by Champion, Rivarola and 
collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
possible misstep of the experiments.

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{figuras/scaling85.eps}
\caption{Ionization cross section per weakly bound electron using
(a) Eq.~(\ref{eq:nelec}) and (b) Eq.~(\ref{eq:scalingCDW}).}
\label{fig:newscaling}
\end{figure}
Figure 4a shows $\sigma_{e}$ calculated with the CDW as a function of 
the impact energy for different projectile charges computed with the 
SSM for the seventeen molecular targets displayed in 
Table~\ref{tab:families}. The universality with $Z$ is the one provided 
by Born approximation, i.e., $\sigma _{e}(Z)=Z^{2}\sigma_{e}(Z=1)$, 
and it holds for large impact velocities, as shown Figure 4a.
Of course, for lower impact velocities, the CDW breaks the behavior of 
the $Z^{2}$ rule. Although the Toburen rule holds for high energies, 
its performance is still not satisfactory: the universal band is quite 
broad. The departure of our theoretical 
results from the Toburen rule can be easily explained by the fact that 
our atomic cross sections $\sigma_{\alpha}$ behave differently for 
each atom in terms of the projectile charges. By inspecting Figure 1, 
one can easily see that the rule $\sigma_{\alpha}/\nu_{\alpha}\sim
\sigma_{e}$ is not well satisfied by the CDW. A much better general 
atomic rule is given by
\begin{equation}
\sigma_{e}^{\text{CDW}}=\frac{\sum\limits_{\alpha}
n_{\alpha}\sigma_{\alpha}^{\text{CDW}}}{\sum\limits_{\alpha}n_{\alpha}
\nu_{\alpha}^{\text{CDW}}},
\label{32} 
\end{equation}
where 
\begin{equation}
\nu_{\alpha }^{\text{CDW}} \sim\left\{ 
\begin{array}{ll}
4,\ \ \  & \text{for C, N, and O,} \\ 
4.5,\ \  & \text{for P and S}
\end{array}
\right. 
\label{eq:scalingCDW}
\end{equation}
and, obviously, $\nu_{\text{H}}^{\text{CDW}}=1$. The cross sections 
$\sigma_{e}^{\text{CDW}}$ are plotted in Figure~4b. A much better sharp 
band is observed, especially at high energy, where the theory is 
expected to work. It will be interesting for experiments to cross-check 
this theoretical prediction.

@@

Extending the simple stoichiometric model for the mean electron energy
calculation, it results
\begin{equation}
\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
\label{70}
\end{equation}
For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu, we obtain 
$\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
experimental values 
on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
52.2 eV, respectively. Just to stress the importance of the projectile 
charge, for O$^{8+}$ on water, at the same impact energy 1 MeV/amu, 
we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
larger than 
proton impact result. It is worth noting that there should not be any 
difference if the calculations were carried in first Born approximation. 
We will came back on this issue later.

@@

As mentioned before, secondary electrons contribute to the total damage. 
Then, not only is the ejection energy important but also the angle 
of emission. Once again, we can consider the single differential cross 
section in terms of the ejected electron solid angle $\Omega$, 
$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution function, 
and the mean angle $\overline{\theta}_{\alpha}$ can be defined as
\begin{equation}
\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
{\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
\end{equation}
Figure 6 shows $\overline{\theta}_{\alpha}$ for our six elements of 
interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
with $Z$ is observed. It is a general belief~\cite{Rudd1992} that the 
angular dispersion of emitted electrons are nearly isotropic. This effect 
is caused by the insignificant angular anisotropy of sub-50-eV yield. 
A typical value for the ejection angle considered in the literature is 
$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
it is quite correct in the range of validity of the first Born 
approximation for any target. But, when a distorted wave approximation 
is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
in the intermediate energy region, as observed in Figure 6. 
For example, for C$^{6+}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
about half of the value obtained with the first Born approximation. 
This correction should close the damage to the forward direction.

@@

\begin{figure}[H]
\centering
%\includegraphics[width=0.95\textwidth]{energylevels/DNA.eps}
\includegraphics[width=0.95\textwidth]{DNA.eps}
\end{figure}

@@

We now return to the calculation of the mean electron energy of H$^{+}$ 
and He$^{2+}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. If we 
consider that the residual charge of each hydrogen in water is 
$q_{\text{H}}=+0.35$~\cite{rappe1991}, which implies that on oxygen we have a 
residual charge of $q_{\text{O}}=-0.7$, we could re-write the formula of water 
using Eq.~(\ref{120}) as H$_{1.3}$O$_{1.17}$ by considering 
$n_{\text{O}}^{\text{CDW}}\simeq 4$ and 
$n_{\text{H}}^{\text{CDW}}\simeq 1$. Recalculating mean electron energy 
by impact of H$^{+}$ and He$^{2+}$ on water at 1 MeV/amu, we obtain
$\overline{E}_{\text{H}_2\text{O}}=46.2$ and 47.6 eV. Our results 
are 10\% apart from the experimental values: 51.5 and 
52.2~eV~\cite{pimblott2007}, respectively, which is not bad considering 
the simplicity of our model.

Another parameter that can computed within our model is the fraction of
energy carried by the electron $f$, which is defined as
\begin{equation}
f=\frac{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}(\sigma_{\alpha}
\overline{E_{\alpha}}+\sum\limits_{nl}\sigma_{\alpha nl}E_{\alpha nl})}\,.
\label{90}
\end{equation}
Using our shell-to-shell ionization cross sections 
$\sigma_{\alpha nl}$~\cite{miraglia2019}, and atomic binding energies of 
the atom $\alpha$, $E_{\alpha nl}$~\cite{clementi}, we obtain 
$f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{2+}$, 
which differ from the respective experimental values $f=0.81$ and $0.80$.

The difference between our calculations and the experiments could be 
attributed to the binding energy values of the molecular water~12.65 eV 
and its atomic components, H (13.6 eV) and O (17.19 eV). This theoretical
discrepancy goes beyond our independent atom approximation and so it 
cannot be accounted for by our model. Once again, we could estimate this 
contribution by resorting to the stoichiometric model. We can make an 
asses for a maximum difference per molecule of water as
\begin{equation}
\delta E=(13.6-12.65)\times1.17+(17.19-12.65)\times1.3=7\,\text{eV}  
\label{80}
\end{equation}
Most of this energy should be transfer to the kinetic energy of the 
emitted electron. Thus, by adding 7 eV to the previous values, we obtain
$\overline{E}_{\text{H}_2\text{O}}=53.2$ and 54.6 eV for H$^{+}$ and 
He$^{2+}$ on water at 1 MeV/amu, respectively, which are much closer to
the experimental values. If we add $\delta E$ to the numerator of 
Eq.~(\ref{90}), we obtain $f=0.81$ and $0.80$, in perfect agreement with 
the experiments (see Table 1 of Ref.~\cite{pimblott2007}).

@@

We calculated ionization cross sections by impact of antiprotons, 
H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$ for seventeen 
molecules containing H, C, N, O, P and S with the CDW method. The 
importance of the influence of $Z$ was observed in the mean energy 
$\overline{E}_{\alpha}$ and angle $\overline{\theta}_{\alpha}$. 
For a given target $\alpha$, as $Z$ increases, $\overline{E}_{\alpha}$ 
increases, but $\overline{\theta}_{\alpha}$ decreases. At high impact 
energy, say larger than 1 MeV/amu, these values converge to the Born 
approximation, which embodies the simple $Z^{2}$ law. The seventeen 
molecules selected were investigated using the simple stoichiometric 
model. Results for six DNA bases were presented and compared with the 
sparse available experiments. We explore the rule of Toburen which scales 
all the molecular ionization cross section when divided by the number of 
weakly bound valence electrons $\nu_{\alpha}$ given by Eq.~(\ref{27}). 
We found the rule scales much better when normalizing our theoretical 
ionization cross sections to the number $\nu_{\alpha}^{\text{CDW}}$ 
given by Eq.~(\ref{eq:scalingCDW}). Finally, we attempt to improve the 
stoichiometric model by using the Mulliken charge to define a new model 
containing fractional rather than integer proportions. No substantial 
correction was found, which indicates that the SSM works quite well.
By inspecting the molecular binding energy from quantum mechanical 
structure calculations, we were able to understand the values defined
for $\nu_{\alpha}^{\text{CDW}}$.

@@

\bibitem{miraglia2009} 
J. E. Miraglia, Ionization of He, Ne, Ar, Kr, and Xe
by proton impact: Single differential distributions. Phys Rev A \textbf{79},
022708 (2009).

@@

\bibitem{miraglia2019} 
J. E. Miraglia. Shell-to-shell ionization cross
sections of antiprotons, H$^{+}$, \ He$^{2+},$ Be$^{4+},$ C$^{6+}$ and O$%
^{8+}$ on H, C, N, O, P, and S atoms To be published Archive 2019.

\bibitem{itoh2013} 
A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D.
Rivarola,~Cross sections for ionization of uracil by MeV-energy-proton
impact,\ Physical Review A 88, 052711 (2013)

@@

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
H. Lekadir, P. F. Weck, and L. C. Tribedi. Ionization of uracil in
collisions with highly charged carbon and oxygen ions of energy 100 keV to
78 MeV.\ \ Phys Rev A 85, 032711 (2012).

\bibitem{toburen1975} 
W. E. Wilson and L. H. Toburen. Electron emission from
proton ---hydrocarbon-molecule collisions at 0.3---2.0 MeV. PHYSICAL REVIEW
A\ 11 1303 (1975).

@@

\bibitem{lee2003} 
Jung-Goo Lee, Ho Young Jeong, and Hosull Lee, Charges of
Large Molecules Using Reassociation of Fragments. Bull. Korean Chem. Soc.24\
2003, 369 .

>>>>

Then, by implementing the SSM and the CDW --instead of the first Born 
approximation--, we calculate ionization cross-section of several 
molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$,\ and O$^{+8}$. Furthermore, 
in Section 3, we investigate different DNA and RNA molecules
such as adenine, cytosine, guanine, thymine, uracil, and also DNA 
backbone.

@@

In Figure 1, we report our total ionization results for the six 
essential elements by the impact of six different projectiles: 
antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
To reduce the resulting 36 magnitudes into a single consistent 
figure, we considered the fact that in the first Born approximation
the ionization cross-section scales with the square of the projectile 
charge, $Z^{2}$. The values of the impact energies considered 
range between 0.1 to 10 MeV/amu, where the CDW is supposed 
to hold. In fact, for the highest projectile charges the minimum 
impact energy where the CDW is expected to be valid could be 
higher than 100 KeV. Moreover, we corroborated that the first Born 
approximation provides quite reliable results only for energies higher 
than a couple of MeV/amu. We use the same color to indicate the 
projectile charge throughout the figures of this work: dashed-red, 
solid-red, blue, magenta, olive and orange for antiprotons, 
H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$, respectively. 
Notably, there is no complete tabulation of ionization of atoms by 
the impact of multicharged ions. We hope that the ones presented 
in this article will be of help for future works.
\begin{figure}
\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
\caption{.}
\label{eq:atomscaling}
\end{figure}

@@

Lets us consider a molecule $M$ composed by $n_{\alpha}$ atoms of the
element $\alpha$, the SSM describes the total ionization cross section 
of the molecule $\sigma_{M}$ as a simple sum of ionization cross 
sections of the isolated atoms $\sigma_{\alpha}$, 
\begin{equation}
 \sigma_{M}=\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}\,.  
 \label{eq:sumion}
\end{equation}
We divided sixteen molecular targets of our interest in three families. 
The classification defined is given in Table~\ref{tab:families}.
\begin{table}
\begin{center}
\begin{tabular}{|p{0.06\textwidth}|p{0.62\textwidth}|}
\hline
 CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, and C$_6$H$_6$ \\
\hline
 CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, and CH$_5$N \\
\hline
 \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
                        cytosine (C$_4$H$_5$N$_3$O), \\
     & guanine (C$_5$H$_5$N$_5$O), thymine (C$_5$H$_6$N$_2$O$_2$), \\
     & uracil (C$_4$H$_4$N$_2$O$_2$), tetrahydrofuran (C$_4$H$_8$O), \\
     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
     & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
\hline
\end{tabular}
\caption{Seventeen molecular targets of our interest classified in three 
families.}
\label{tab:families}
\end{center}
\end{table}

In Figure 2, we report the total ionization cross sections by the 
impact of multicharged ions for the four fundamental DNA components: 
adenine, cytosine, guanine and thymine. Our reports for uracil and 
DNA backbone containing P are given in Figure 3. For adenine, the 
agreement with the experimental data available in our range of validity 
is quite good. For uracil, we have a puzzling situation: our results 
show good agreement with the experiments by proton impact of Itoh 
{\it et al.}~\cite{itoh2013}, but for the same target our theory fails 
by a factor of two for the impact of C$^{+4}$ and O$^{+6}$ ions. 
Nonetheless, it should be stated that our theoretical results coincide 
with calculations by Champion, Rivarola and 
collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
possible misstep of the experiments.

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{figuras/molscaling85.eps}
\caption{Ionization cross section per weakly bound electron using
(a) Eq.~(\ref{eq:nelec}) and (b) Eq.~(\ref{eq:scalingCDW}).}
\label{fig:newscaling}
\end{figure}
Figure 4a shows $\sigma_{e}$ calculated with the CDW as a function of 
the impact energy for different projectile charges computed with the 
SSM for the seventeen molecular targets displayed in 
Table~\ref{tab:families}. The universality with $Z$ is the one provided 
by Born approximation, i.e., $\sigma _{e}(Z)=Z^{2}\sigma_{e}(Z=1)$, 
and it holds for large impact velocities, as shown Figure 4a.
Of course, for lower impact velocities, the CDW breaks the behavior of 
the $Z^{2}$ rule. Although the Toburen rule holds for high energies, 
its performance is still not satisfactory: the universal band is quite 
broad. The departure of our theoretical 
results from the Toburen rule can be easily explained by the fact that 
our atomic cross sections $\sigma_{\alpha}$ behave differently for 
each atom in terms of the projectile charges. By inspecting Figure 1, 
one can easily see that the rule $\sigma_{\alpha}/\nu_{\alpha}\sim
\sigma_{e}$ is not well satisfied by the CDW. A much better general 
atomic rule is given by
\begin{equation}
\sigma_{e}^{\text{CDW}}=\frac{\sum\limits_{\alpha}
n_{\alpha}\sigma_{\alpha}^{\text{CDW}}}{\sum\limits_{\alpha}n_{\alpha}
\nu_{\alpha}^{\text{CDW}}},
\label{32} 
\end{equation}
where 
\begin{equation}
\nu_{\alpha }^{\text{CDW}} \sim\left\{ 
\begin{array}{ll}
4,\ \ \  & \text{for C, N, and O,} \\ 
4.5,\ \  & \text{for P and S}
\end{array}
\right. 
\label{eq:scalingCDW}
\end{equation}
and, obviously, $\nu_{\text{H}}^{\text{CDW}}=1$. The cross sections 
$\sigma_{e}^{\text{CDW}}$ are plotted in Figure~4b. A much better sharp 
band is observed, especially at high energy, where the theory is 
expected to work. It will be interesting for experiments to cross-check 
this theoretical prediction.

@@

Extending the simple stoichiometric model for the mean electron energy
calculation, it results
\begin{equation}
\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
\label{70}
\end{equation}
For impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain 
$\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
experimental values 
on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
52.2 eV, respectively. Just to stress the importance of the projectile 
charge, for O$^{+8}$ on water, at the same impact energy 1 MeV/amu, 
we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
larger than proton impact result. It is worth noting that there should 
not be any difference if the calculations were carried in first Born 
approximation. We will came back on this issue later.

@@

As mentioned before, secondary electrons contribute to the total damage. 
Then, not only is the ejection energy important but also the angle 
of emission. Once again, we can consider the single differential cross 
section in terms of the ejected electron solid angle $\Omega$, 
$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution function, 
and the mean angle $\overline{\theta}_{\alpha}$ can be defined as
\begin{equation}
\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
{\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
\end{equation}
Figure 6 shows $\overline{\theta}_{\alpha}$ for our six elements of 
interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
with $Z$ is observed. It is a general belief~\cite{Rudd1992} that the 
angular dispersion of emitted electrons are nearly isotropic. This effect 
is caused by the insignificant angular anisotropy of sub-50-eV yield. 
A typical value for the ejection angle considered in the literature is 
$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
it is quite correct in the range of validity of the first Born 
approximation for any target. But, when a distorted wave approximation 
is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
in the intermediate energy region, as observed in Figure 6. 
For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
about half of the value obtained with the first Born approximation. 
This correction should close the damage to the forward direction.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
\end{figure}

@@

We now return to the calculation of the mean electron energy of H$^{+}$ 
and He$^{+2}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. If we 
consider that the residual charge of each hydrogen in water is 
$q_{\text{H}}=+0.35$~\cite{rappe1991}, which implies that on oxygen we 
have a residual charge of $q_{\text{O}}=-0.7$, we could re-write the 
formula of water using Eq.~(\ref{120}) as H$_{1.3}$O$_{1.17}$ by 
considering 
$n_{\text{O}}^{\text{CDW}}\simeq 4$ and 
$n_{\text{H}}^{\text{CDW}}\simeq 1$. Recalculating mean electron energy 
by impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain
$\overline{E}_{\text{H}_2\text{O}}=46.2$ and 47.6 eV. Our results 
are 10\% apart from the experimental values: 51.5 and 
52.2~eV~\cite{pimblott2007}, respectively, which is not bad considering 
the simplicity of our model.

Another parameter that can computed within our model is the fraction of
energy carried by the electron $f$, which is defined as
\begin{equation}
f=\frac{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}(\sigma_{\alpha}
\overline{E_{\alpha}}+\sum\limits_{nl}\sigma_{\alpha nl}E_{\alpha nl})}\,.
\label{90}
\end{equation}
Using our shell-to-shell ionization cross sections 
$\sigma_{\alpha nl}$~\cite{miraglia2019}, and atomic binding energies of 
the atom $\alpha$, $E_{\alpha nl}$~\cite{clementi}, we obtain 
$f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{+2}$, 
which differ from the respective experimental values $f=0.81$ and $0.80$.

The difference between our calculations and the experiments could be 
attributed to the binding energy values of the molecular water~12.65 eV 
and its atomic components, H (13.6 eV) and O (17.19 eV). This theoretical
discrepancy goes beyond our independent atom approximation and so it 
cannot be accounted for by our model. Once again, we could estimate this 
contribution by resorting to the stoichiometric model. We can make an 
asses for a maximum difference per molecule of water as
\begin{equation}
\delta E=(13.6-12.65)\times1.17+(17.19-12.65)\times1.3=7\,\text{eV}  
\label{80}
\end{equation}
Most of this energy should be transfer to the kinetic energy of the 
emitted electron. Thus, by adding 7 eV to the previous values, we obtain
$\overline{E}_{\text{H}_2\text{O}}=53.2$ and 54.6 eV for H$^{+}$ and 
He$^{+2}$ on water at 1 MeV/amu, respectively, which are much closer to
the experimental values. If we add $\delta E$ to the numerator of 
Eq.~(\ref{90}), we obtain $f=0.81$ and $0.80$, in perfect agreement with 
the experiments (see Table 1 of Ref.~\cite{pimblott2007}).

@@

We calculated ionization cross sections by impact of antiprotons, 
H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$ for seventeen 
molecules containing H, C, N, O, P and S with the CDW method. The 
importance of the influence of $Z$ was observed in the mean energy 
$\overline{E}_{\alpha}$ and angle $\overline{\theta}_{\alpha}$. 
For a given target $\alpha$, as $Z$ increases, $\overline{E}_{\alpha}$ 
increases, but $\overline{\theta}_{\alpha}$ decreases. At high impact 
energy, say larger than 1 MeV/amu, these values converge to the Born 
approximation, which embodies the simple $Z^{2}$ law. The seventeen 
molecules selected were investigated using the simple stoichiometric 
model. Results for six DNA bases were presented and compared with the 
sparse available experiments. We explore the rule of Toburen which scales 
all the molecular ionization cross section when divided by the number of 
weakly bound valence electrons $\nu_{\alpha}$ given by Eq.~(\ref{27}). 
We found the rule scales much better when normalizing our theoretical 
ionization cross sections to the number $\nu_{\alpha}^{\text{CDW}}$ 
given by Eq.~(\ref{eq:scalingCDW}). Finally, we attempt to improve the 
stoichiometric model by using the Mulliken charge to define a new model 
containing fractional rather than integer proportions. No substantial 
correction was found, which indicates that the SSM works quite well.
By inspecting the molecular binding energy from quantum mechanical 
structure calculations, we were able to understand the values defined
for $\nu_{\alpha}^{\text{CDW}}$.

@@

\bibitem{miraglia2009} 
J. E. Miraglia, Ionization of He, Ne, Ar, Kr, and Xe
by proton impact: Single differential distributions. 
Phys. Rev. A \textbf{79}, 022708 (2009).

@@

\bibitem{miraglia2019} 
J. E. Miraglia. Shell-to-shell ionization cross
sections of antiprotons, H$^{+}$, He$^{+2},$ Be$^{+4},$ C$^{+6}$ and 
O$^{+8}$ on H, C, N, O, P, and S atoms To be published Archive 2019.

\bibitem{itoh2013} 
A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D.
Rivarola, Cross sections for ionization of uracil by MeV-energy-proton
impact, 
Phys. Rev. A 88, 052711 (2013)

@@

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
H. Lekadir, P. F. Weck, and L. C. Tribedi. Ionization of uracil in
collisions with highly charged carbon and oxygen ions of energy 100 keV to
78 MeV. 
Phys. Rev. A 85, 032711 (2012).

\bibitem{toburen1975} 
W. E. Wilson and L. H. Toburen. Electron emission from
proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
Phys. Rev. A 11, 1303 (1975).

@@

\bibitem{lee2003} 
Jung-Goo Lee, Ho Young Jeong, and Hosull Lee, Charges of
Large Molecules Using Reassociation of Fragments. 
Bull. Korean Chem. Soc.24 2003, 369 .
